Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-11 paper.tex
chore: comment for @LukasEsterle

Let $\Gamma$ be the aggregate program that runs against $G_t$.  \lukas{$G_t$ is not defined. also, not sure what `runs against' means - take $G_t$ as input?}

@@

The evaluation of $\Gamma$  produce a field value $\theta^v_t$ for each node $v$ in $G_t$. 

>>>>

Let $\Gamma$ be the aggregate program that runs take $G_t$ as input.  \lukas{$G_t$ is not defined. also, not sure what `runs against' means - take $G_t$ as input?}
\ga{In the problem formalization, I defined $G_t$, but it may be more appropriate to define it directly in the GNN, as suggested. I made this choice since GNNs typically only receive a graph as input, without regard for time, I included the definition of $G_t$ in the problem formalization as it pertains to the dynamics of the overall system. Specifically, when discussing the system's dynamics at a given time t, it's necessary to define the corresponding graph. I hope this clarifies my reasoning. Let me know!}

@@

The evaluation of $\Gamma$ produces a field value $\theta^v_t$ for each node $v$ in $G_t$. 
